```{r, include=FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
devtools::load_all()
```
# spitcastr

[![Travis](https://img.shields.io/travis/sboysel/spitcastr.svg?style=flat-square)](https://travis-ci.org/sboysel/spitcastr)
[![Codecov](https://img.shields.io/codecov/c/github/sboysel/spitcastr.svg?style=flat-square)](https://codecov.io/github/sboysel/spitcastr)
[![GitHub
license](https://img.shields.io/github/license/sboysel/spitcastr.svg?style=flat-square)](https://github.com/sboysel/spitcastr/blob/master/LICENSE)

An `R` client for the [Spitcast Surf Forecast
API](http://www.spitcast.com/api/docs/).

## Usage
Install `spitcastr`
```{r install, eval=FALSE}
# install.packages("devtools")
devtools::install_github("sboysel/spitcastr")
library(spitcastr)
```
### County
List the spots in a county
```{r county_spots}
library(dplyr)
county(item = "spots", county_name = "Orange County") %>%
  dplyr::tbl_df()
```
List swell forecasts for a particular county
```{r county_swell}
county(item = "swell", county_name = "Orange County") %>%
  dplyr::tbl_df()
```
Get tide predictions for a particular county
```{r county_tide}
county(item = "tide", county_name = "Orange County") %>%
  dplyr::tbl_df()
```
Get water temperature for a particular county
```{r county_temp}
county(item = "temp", county_name = "Orange County") %>%
  dplyr::tbl_df()
```
Get wind speed predictions for a particular county
```{r county_wind}
county(item = "wind", county_name = "Orange County") %>%
  dplyr::tbl_df()
```
### Spots
List all spots
```{r spot_all, warning=FALSE, message=FALSE}
spot(item = "all") %>%
  dplyr::tbl_df() %>%
  dplyr::filter(county_name == "Santa Barbara") 
```
Get the forecast for a specific spot
```{r spot_forecast}
spot(item = "forecast", spot_id = 183) %>%
  dplyr::tbl_df()
```
List spot near your location
```{r spot_nearby}
spot(item = "nearby") %>%
  dplyr::tbl_df()
```
List neighbors of a given spot
```{r spot_neighbors}
spot(item = "neighbors", spot_id = 1, direction = "above") %>%
  dplyr::tbl_df()
```
Search for a spot with a sequence of parameters 
```{r spot_search_forecast}
spot(item = "search", size_min = 3, size_max = 8, shape_min = 1) %>%
  dplyr::tbl_df()
```
List top spots
```{r spot_top}
spot(item = "top") %>%
  dplyr::tbl_df()
```

## Resources

* [Spitcast Surf Forecast API Documentation](http://www.spitcast.com/api/docs/)

Be sure to checkout [Spitcast](http://www.spitcast.com/) and read the ['fine
print'](www.spitcast.com/api/docs/):

> Public distribution of Spitcast API content must acknowledge Spitcast as
> the content source, and provide a link to Spitcast.com.

> The Spitcast API is available for non-commercial use. Commercial use is 
> possible by prior arrangement.

> The Spitcast API is available for low request volume use. Please cache API 
> responses. Please also make API requests to api.spitcast.com, and NOT to 
> www.spitcast.com.

> The Spitcast API is experimental and is currently offered on an ad hoc basis 
> with no guarantee of uptime or availability of continued service. We reserve 
> the right to disable access to external applications at any time.

